Dissecting Neural Style Transfer

### 2019-05-26 paper/paper.tex
1

The arrays after the initial image are called feature maps, because their value means
``how much a feature x exists at position y and x''.
Take a $1\times64\times512\times512$ feature map for example. There are 64 types of features.
Its [1, 17, 111, 222] element, would then refer to the extent that the 17th type feature exists
at the position of the 222th column of the 111th row. This ``extent'' could also be negative.

@@

Now we wonder, could we achieve similar results with other ways to compare 
distribution of features?
One approach would be to consider the \emph{comparison} as a whole to find 
substitutes. 
For example, minimising the mean square errors between two Gram matrices could be seen as 
a special case for minimising a Maximum Mean Discrepancy, which means other Maximum Mean Discrepacies
could be used \cite{MMD}.
For us, it seemed more natural to consider substitutes for the process itself of 
transforming a feature map into a Gram matrix. 
That is, we will consider other
mappings that remove the spatial information of where features are but retains
the distribution of features, like a histogram.
We will call such functions ``\emph{dislocators}'' in the remaing part of this work.
Unfortunately, the word ``dislocate'' would give the connotation of moving something to somewhere else.
However, the word ``locator'' means something that provides spatial information,
so calling somthing that removes spatial information a ``dislocator'' is still plausible.

Some ``dislocator'' functions we tried are

>>>>

The arrays after the initial image are called \emph{feature maps}, because their value means
``how much a feature x exists at position y and x''.
Take a $1\times64\times512\times512$ feature map for example. There are 64 types of features.
Its [1, 17, 111, 222] element, would then refer to the extent that the 17th type feature exists
at the position of the 222th column of the 111th row. This ``extent'' could also be negative.

@@

Now we wonder, could we achieve similar results with other ways to compare 
distribution of features?
One approach would be to consider the \emph{comparison} as a whole to find 
substitutes. 
For example, minimising the mean square errors between two Gram matrices could be seen as 
a special case for minimising a Maximum Mean Discrepancy, which means other Maximum Mean Discrepacies
could be used \cite{MMD}.
For us, it seemed more natural to consider substitutes for the process itself of 
transforming a feature map into a Gram matrix. 
That is, we will consider other
mappings that remove the spatial information or where features are in a feature map but retain
the distribution of features, like a histogram.
Such functions need to be differentiable as well, otherwise they would render the 
optimisation infeasible.

We will call such functions ``\emph{dislocators}'' in the remaing part of this work.
Unfortunately, the word ``dislocate'' would give the connotation of moving something to somewhere else.
Nevertheless, the word ``locator'' means something that provides spatial information,
so calling somthing that removes spatial information a ``dislocator'' is still reasonable.

Other ``dislocator'' functions whose output somehow describe the 
distribution of features in their input should then work as substitutes
for computing Gram matrices.
The first few simplistic ``dislocator'' functions we tried are listed here.
\begin{enumerate}
\item Scaled sum of the responses all over the place for each feature.
That is, for an $1\times64\times256\times256$ feature map,
we compute an $1\times64$ array where each element is the sum of the
$256\times256$ elements from the input.
The whole array is then scaled to one over the total number of elements of the input feature map.
\item Scaled sum of element-wise squares of the responses over the place for each feature.
Other than an additional element-wise squaring, it is identical to the previous one.
\item Scaled sum of absolute values of the responses over the place for each feature.
\end{enumerate}
